\chapter{Introduction}

% Last updated: 20191119

My previous Lessons From Sessions Special Report small book was
called Ten Thousand in Ten Weeks. I loved the title of that
report and of course the dollars won over that period.
This report has an even more exciting and attention-grabbing title: Seven
Thousand in Seven Hours. It tells the story of my most recent big
poker session, and the biggest win of my life. Seven thousand dollars
in Seven Hours.

I'm stretching the truth ever so slightly in my title. The session was
a touch over Seven Hours, it went from 7:10pm until 2:25am so it's
seven-and-a-quarter hours. And my winnings didn't quite hit \$7000, in
fact I ended \$6700 to the good. That's 95.7\% of \$7000 so close enough
for the title. Seven Thousand in Seven Hours sounds much better as a
report title than ``a bit under seven thousand in a bit over seven
hours''.

The session was at Canberra Casino, of course. It was the first winning
session of my Summer 2019 Campaign. Before we get to the huge win, I
need to write about the bad start to that campaign and a Sunday night
life episode that I wish had never happened.

% \section*{name} : an unnumbered section that won't appear in the contents


%% \section*{About the author}

% FIXME: Back cover copy?

%% Stuart Cooper wrote the ``Doctor Straight'' column, primarily
%% on Pub Poker Tournaments, in the Australian Poker Weekly newspaper
%% for the entirety of the newspaper's two-and-a-half year run.
%% In the 131 issues of the paper he produced 105 columns.

%% Stuart has three major tournament wins (50\$ buyin, 100+ players)
%% to his credit and many small nightly tournament wins.

%% He lives and plays poker in Sydney.
