\chapter{A Losing Start}

At the end of Ten Thousand in Ten Weeks, I anounced the start of my
Summer 2019 campaign, lasting until 31st December 2019. I set myself a
target of \$8000 profit in eleven weeks; which is \$728 a week or just
over \$100 a day. The campaign started terribly and by week four I had
four losses in a row and was down \$2300! I was on track for a ten
thousand dollar \textbf{loss} in eleven weeks, giving back my entire
winnings from the Spring Campaign.

\section*{A big Canberra loss}

The Campaign started with a trip to Casino Canberra on Friday 25th
October. Canberra have dropped their old 1-2-5 \$200-\$UNLIMITED buyin
game, and the PLO big game there is now 5-5 \$200-\$2,000 buyin. I
liked the 1-2-5 format although the unlimited buyin did let some
megarich maniacs simply rebuy and cover the table when they lost their
stacks. \$2000 should be enough to play with in a game with the big
blind of \$5.

My first buyin of \$200 goes well early, getting to \$1,300. I then
suffer a turned nut straight losing to a board pair on the river. I'm
then made to call big bets on the flop and turn with a nut flush draw,
but it misses and I'm back to \$230 then busted soon after. My second
buyin doesn't last and the third buyin gets annoyingly unlucky. I've
got A-J-5-5 to a flop of 755. I get all in against K-Q-Q-5 who spikes
a Queen on the turn to leave me drawing dead. He only had four outs
when the money went in but I can't blame him for jamming his money in
against my hand.

I'm soon in for my fourth buyin, which is the most interesting buyin
of the night. I get my stack up to \$1980 with a few winning hands and
then win a megapot against Maths David. I hold Q-T-9-9 and flop the
straight world on a flop of K-Jc-8c. Maths David has Kc-K-Tc-4 for the
top set and good flush draw but I crack him on the runout KJ8TA; no
clubs and no repeaters. A nice break for me; because top set flush
draw is always a favourite.

My stack is now a huge \$4,080 and although I'm into my fourth buyin
and in for \$800 I'm looking at a massive \$3,200 win, if I cash out
now. Unfortunately, I push on.


% FIXME finish this section

\section*{The Sunday Night Life Episode}

I wrote my car off by running up the back of another car on King
George's Road in Beverly Hills on Sunday night 3rd November 2019.
I was rushing from a home game in Sylvania to pick up my girlfriend in
Parramatta; it was pouring rain and a Deliveroo motorbike
rider dickhead (are there any other kind?) had pulled out without
looking, causing a right lane guy to hit him and stop dead and causing
me to run up the back of the right lane guy. Yes I was driving too
fast for the conditions and yes I was at fault but the cops didn't
issue any tickets and I settled with the other car driver.

I'd only been at the Sylvania Home Game for five minutes; it was a
game I'd been invited to many times and I felt I should ``put in an
appearance'' even though I knew I'd have to leave it by 930pm to get
to Parramatta by 10pm. There's no point turning up to a poker game for
five minutes and expecting even hoping to lose a single buyin; it's
actually extremely rude and you're better off not turning up at all.

You don't know how much you use your car and need your car until you
haven't got one. Being without a car is extremely annoying; both from
a shopping, social and and poker point of view. Just about the only
event I was easily able to get to from my place in Carlingford by
public transport was a Saturday raceday at Rosehill Gardens.

My car was on its last legs and I was going to get a new car in March
2020 once the rego on the old car had expired. I'm now bringing
forward those plans by a few months.
